Computing Entropies With Nested Sampling

### 2017-05-29 paper/ms.tex
Updated results

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\boldeta}{\boldsymbol{\eta}}
\newcommand{\n}{\boldsymbol{\eta}}
\newcommand{\depth}{\textnormal{depth}}

@@

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for each of the three
runs. The results are:
\begin{align}
H_{\tau}    &= 6.243  \pm 0.024 \\
H_{\d}      &= 712.43 \pm 0.35   \\
H_{\tau,\d} &= 715.81 \pm 0.34
\end{align}

>>>>

\renewcommand{\d}{\boldsymbol{d}}
\newcommand{\todo}{\color{orange} \bf}
\newcommand{\query}{\color{green} \bf}
\newcommand{\x}{\boldsymbol{\theta}}
\newcommand{\bphi}{\boldsymbol{\phi}}
\newcommand{\boldeta}{\boldsymbol{\eta}}
\newcommand{\n}{\boldsymbol{\eta}}
\newcommand{\depth}{(\textnormal{depth})}

@@

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the depths
for $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of $L=0.001$
for $\tau$, $0.001\sqrt{101}$ for $\d$, and $0.001\sqrt{102}$ for
the joint run. The results were:
\begin{align}
\depth_{\tau}    &= 6.216  \pm 0.025 \\
\depth_{\d}      &= 480.13 \pm 0.32   \\
\depth_{\tau,\d} &= 479.96 \pm 0.31
\end{align}
